---
title: "Information and Communications Technology (ICT) and Emigration Flows"
subtitle:  "Final Project Proposal"
author: "Ayra Rowena Reyla and Ana Cecilia Montes"
date: "15 October 2015"
output: pdf_document

toc: true
theme: united
highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Introduction 
More than 200 million individuals now live outside of their home country and few countries are unaffected by international migration (Martin, 2014).International emigration is part of a transnational shift that is currently reshaping societies and politics around the globe. There have been multiple waves of emigration through the decades, and it is no surprise that the increase of communication and advances made in technology have radically altered the world we live in. Globalization has increased the interactions in various financial markets, knowledge sharing, social media and web browsing. 

This paper uses data on trends in International Migrant Stock produced by the United Nations. The data contains information from 232 countries and provides the number of migrants by destination and country of origin for four periods of time; 1990, 2000, 2010, and 2013. Moreover, to account for technology diffusion we will use World Bank indicators on the number of Internet users and the number of cellular mobile subscriptions for each country. 

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
